\subsection{RQ1: How well can we model the receiver of a pass?}\label{RQ2-results}

\textbf{Our model can predict the receiver of a pass with a top-1, top-3 and top-5 accuracy of 50\%, 84\%, and 94\%, respectively, when we exclude false passes (i.e., passes to the other team).}
Table~\ref{tab:performance-accurate-passes} shows the performance of our model when we exclude false passes. 
The ``Back-field'', ``Middle-field'', ``Front-field'' and ``Overall'' columns show the performance of our model for back-field passes, middle-field passes, front-field passes and all passes, respectively. 
A top-3 accuracy of 84\% for all passes means that the actual receiver of a pass has a 84\% chance to appear in our top-3 predicted candidates.
The MRR value for all passes is 0.68, which means on average, the correct receiver is ranked $1.5$th (i.e., 1/0.68) out of 10 or less receiver candidates (i.e., all teammates of the sender).

%\setlength{\tabcolsep}{3pt}
\begin{table}[!t]
\caption{The accuracy of our model for predicting the receiver of a pass (excluding false passes).}
\centering
\renewcommand{\tabcolsep}{3pt}
\begin{tabular}{lcccc}
  \toprule
  & Back-field & Middle-field & Front-field & Overall \\
  \midrule
  Top-1 accuracy & 53\% & 46\% & 55\% & 50\% \\
  Top-3 accuracy & 84\% & 81\% & 91\% & 84\% \\
  Top-5 accuracy & 93\% & 93\% & 97\% & 94\% \\
  MRR & 0.70 & 0.66 & 0.73 & 0.68 \\
  \bottomrule
\end{tabular}
\label{tab:performance-accurate-passes}
%\vspace{-0.4cm}
\end{table}

\begin{table}[!t]
\caption{Comparing the accuracy of our model with baseline models (excluding false passes).}
\centering
\renewcommand{\tabcolsep}{3pt}
%\begin{threeparttable}
\begin{tabular}{lcccc}
  \toprule
  & LightGBM & RandomGuess & NearestPass & NearestForwardPass \\
  \midrule
  Top-1 accuracy & \textbf{50\%} & 10\% & 33\% & 27\% \\
  Top-3 accuracy & \textbf{84\%} & 30\% & 70\% & 54\% \\
  Top-5 accuracy & \textbf{94\%} & 50\% & 86\% & 71\% \\
  MRR & \textbf{0.68} & 0.29 & 0.55 & 0.47 \\
  \bottomrule
\end{tabular}
%\begin{tablenotes}
%\item[1] Randomly guess a candidate receiver.
%\item[2] A model that always passes the ball to the nearest teammate of the sender.
%\item[3] A model that always passes the ball to the nearest teammate that is in the forward direction relative to the sender.
%\end{tablenotes}
%\end{threeparttable}
\label{tab:comparing-performance-accurate-passes}
%\vspace{-0.4cm}
\end{table}

\textbf{Our model can predict the receiver of a pass with a top-1, top-3 and top-5 accuracy of 41\%, 70\%, and 81\%, respectively, when we consider all passes.}
Table~\ref{tab:performance-all-passes} shows the performance of our model when we consider all passes (including false passes). 
The performance of our model decreases when we consider false passes (i.e., passes to the other team). 
False passes are very difficult to predict because it is not the sender player's intention to pass the ball to the other team. 
The MRR value for all passes is 0.58, which means the correct receiver is averagely ranked $1.7$th (i.e., 1/0.58) out of all 21 or less candidate receivers (i.e., all players excluding the sender).

%\setlength{\tabcolsep}{6pt}
\begin{table}[!t]
%\vspace{-0.2cm}
\caption{The accuracy of our model for predicting the receiver of a pass (considering all passes including passes to the other team).}
\centering
\renewcommand{\tabcolsep}{3pt}
\begin{tabular}{lcccc}
  \toprule
  & Back-field & Middle-field & Front-field & Overall \\
  \midrule
  Top-1 accuracy & 45\% & 38\% & 43\% & 41\% \\
  Top-3 accuracy & 72\% & 68\% & 72\% & 70\% \\
  Top-5 accuracy & 82\% & 80\% & 83\% & 81\% \\
  MRR & 0.61 & 0.56 & 0.60 & 0.58 \\
  \bottomrule
\end{tabular}
\label{tab:performance-all-passes}
%\vspace{-0.4cm}
\end{table}

\begin{table}[!t]
\caption{Comparing the accuracy of our model with baseline models (considering all passes including passes to the other team).}
\centering
\renewcommand{\tabcolsep}{3pt}
%\begin{threeparttable}
\begin{tabular}{lcccc}
  \toprule
  & LightGBM & RandomGuess & NearestPass & NearestForwardPass \\
  \midrule
  Top-1 accuracy & \textbf{41\%} & 5\% & 27\% & 23\% \\
  Top-3 accuracy & \textbf{70\%} & 14\% & 58\% & 45\% \\
  Top-5 accuracy & \textbf{81\%} & 24\% & 71\% & 59\% \\
  MRR & \textbf{0.58} & 0.17 & 0.47 & 0.40 \\
  \bottomrule
\end{tabular}
%\begin{tablenotes}
%\item[1] Randomly guess a candidate receiver.
%\item[2] A model that always passes the ball to the nearest teammate of the sender.
%\item[3] A model that always passes the ball to the nearest teammate that is in the forward direction relative to the sender.
%\end{tablenotes}
%\end{threeparttable}
\label{tab:comparing-performance-all-passes}
%\vspace{-0.4cm}
\end{table}

\textbf{Our model performs better for back-field and front-field passes, while performing worse for middle-field passes.}
Table~\ref{tab:performance-accurate-passes} and Table~\ref{tab:performance-all-passes} also shows the performance of our model for back-field, middle-field and front-field passes, separately.
Surprisingly, the performance of our model is the worst for middle-field passes. A player in the middle area may have more passing options, thereby increasing the difficulty to predict the right receivers.

\textbf{Our model perform better than the baseline models.}
Table~\ref{tab:comparing-performance-accurate-passes} and Table~\ref{tab:comparing-performance-all-passes} compare the performance of our LightGBM model with the RandomGuess, NearestPass, and NearestForwardsPass models which are described in Section~\ref{methodology}.
Our LightGBM model consistently show much better performance than the three baseline models in terms of the top-N accuracy and MRR.
The NearestPass model, which tends to pass the ball to the nearest teammates, achieve a better performance than the NearestForwardPass, which tends to pass the ball to the nearest teammates in the forward direction relative to the sender.
Both of the NearestPass and NearestForwardPass baseline models achieve a much better performance than randomly guessing the receiver of a pass.

%\vspace{-0.4cm}
\hypobox{
Our model can predict the receiver of a pass with a top-1, top-3 and top-5 accuracy of 50\%, 84\%, and 94\%, respectively, when we exclude false passes. Our model performs better when the sender of a pass is in the back or front area of the field.
}