\subsection{RQ2: what are the important factors that explain the receiver of a pass?}\label{RQ3-results}

\textbf{The features that capture the candidate receivers' positions play the most important roles in explaining the receiver of a pass.}
Table~\ref{tab:combined-feature-importance} shows the combined importance of each feature dimension in our model. The combined importance is a sum of the importance scores of all the individual features in a dimension.
The features from the dimension of candidate receiver position, which capture a candidate receiver's position on the pitch and his/her position relative to the teammates and opponents, have the biggest combined importance score in our model.
The team position features, which captures the overall position of the team in control of the ball, are the second important dimension in explaining the receiver of a pass.
The third important feature dimension (i.e., sender position) captures the sender's position on the pitch and his/her position relative to the teammates and opponents.
The passing path features, which captures the characteristics of a passing path (i.e., the path from the sender to a candidate receiver), also play a significant role in explaining the receiver of a pass.

\begin{table}[!t]
\caption{The combined importance of each feature dimension.}
\centering
\renewcommand{\tabcolsep}{3pt}
\begin{tabular}{lc}
  \toprule
  Feature dimension & Combined feature importance \\
  \midrule
  Candidate receiver position & 6723 \\
  Team position & 3493 \\
  Sender position & 2688 \\
  Passing path & 1753 \\
  Game state & 343 \\
  \bottomrule
\end{tabular}
\label{tab:combined-feature-importance}
%\vspace{-0.4cm}
\end{table}

\textbf{The most important features capture the candidate receivers' positions relative to the sender and the opponents.}
Table~\ref{tab:top-10-feature} lists the top ten features that are most important in our model and their respective importance scores.
A full list of our features' important scores is available online\footnotemark[\ref{feature-list}].
%Our online feature list\footnotemark[\ref{feature-list}] shows each feature's importance score in our model.
Among the top 10 important features, there are eight features from the candidate receiver position dimension. %, one from the sender position dimension, and one from the passing path dimension.
%Among the top 20 important features, there are 12 features from the candidate receiver position dimension, four from the sender position dimension, three from the passing path dimension, and one from the team position dimension.
All of the top six features are from the dimension of candidate receiver position, among which three features capture a candidate receiver's relative position to the sender, and the other three features capture a candidate receiver's relative position to the components.
The other two features from the dimension of candidate receiver position capture a candidate receiver's position on the pitch and his/her relative position to the teammates, respectively.
Among the top 10 important features, there are also one from the sender position dimension (i.e., the sender\_closest\_opponent\_dist feature), and one from the passing path dimension (i.e., the min\_pass\_angle feature).

%\setlength{\tabcolsep}{3pt}
\begin{table}[!t]
\caption{The ten most important features and their importance scores.}
\centering
\renewcommand{\tabcolsep}{3pt}
\resizebox{1.0\textwidth}{!} {
\begin{threeparttable}
\begin{tabular}{llcp{6cm}}
  \toprule
  Dimension & Feature & Importance & Description \\
  \midrule
  \specialcell{Receiver\\position\tnote{1}} & \specialcell{receiver\_closest\_\\opponent\_dist} & 715 &  The distance between the candidate receiver and his/her closest opponent \\
  \specialcell{Receiver\\position} & \specialcell{norm\_receiver\_\\sender\_x\_diff} & 660 & Normalized x-axis difference between the candidate receiver and the sender \\
  \specialcell{Receiver\\position} & abs\_y\_diff & 653 & The absolute value of the y-axis difference between the sender and the candidate receiver \\
  \specialcell{Receiver\\position} & distance & 616 & The candidate receiver's distance to the sender \\
  \specialcell{Receiver\\position} & \specialcell{receiver\_closest\_\\opponent\_to\_\\sender\_dist} & 602 & The distance between the sender and the candidate receiver's closest opponent \\
  \specialcell{Receiver\\position} & \specialcell{receiver\_closest\_3\_\\opponents\_dist} & 558 & The average distance between the candidate receiver and his/her three closest opponents \\
  \specialcell{Receiver\\position} & \specialcell{receiver\_to\_center\_\\distance} & 521 & The distance between the candidate receiver and the center of the pitch \\
  \specialcell{Receiver\\position} & \specialcell{receiver\_closest\_3\_\\teammates\_dist} & 508 & The average distance between the candidate receiver and his/her three closest teammates \\
  \specialcell{Sender\\position} & \specialcell{sender\_closest\_\\opponent\_dist} & 498 & The distance between sender and his/her closest opponent \\
  \specialcell{Passing\\path} & min\_pass\_angle & 467 & Pass angles are the angles between the line from the sender to the candidate receiver (i.e., the pass line) and the lines from the sender to the opponents along the pass line. The min\_pass\_angle is the minimum pass angle for a pass line \\
 
  \bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] ``Receiver position'' is short for ``candidate receiver position''.
\end{tablenotes}
\end{threeparttable}
}
\label{tab:top-10-feature}
%\vspace{-0.4cm}
\end{table}

%\vspace{-0.2cm}
\hypobox{
The features that capture the positions of the candidate receivers, in particular, relative to the sender and the opponents, play the most important roles in explaining the receiver of a pass.
}